Evaluating Open Information Extraction for Ontologization of a Thematic Domain

### 2014-07-16 paper/ekaw-2014/ekaw2014.tex
changes almost in place, should be shrunken to 15 pages!

\usepackage{subfigure}
\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{graphicx}
\usepackage[numbers, sectionbib]{natbib}
\usepackage{tabularx}
%\usepackage{float}
\usepackage{afterpage}

@@

%TODO Tables instead of figures where relevant

@@

The second method for the evaluation of concept assignment employs bootstrapping as discussed in sec.~\ref{sec:framework}. This process involves selection of a seedset and determining the number of bootstrapping iterations. For the sake of brevity, we have set the size of seedset to be the same for all the concepts, which is 3. The entities in the seedset are randomly chosen from the ones among the reference data taken from Wikipedia. However, as the bootstrapping process itself can be sensitive to the initial selection of the entities in the seedset, the whole process is repeated 5 times with randomly chosen seedsets. The bootstrapping method is terminated once the size of seedset reaches that of the corresponding concept in the reference data. After every 5 instances added during the process, we measure the overlap ($O$) and residual ($R$) portions of the seedset with respect to the reference data.  Figs.~\ref{fig:qual-object-bootstrapping-carnatic} and \ref{fig:qual-object-bootstrapping-hindustani} show their mean over 5 runs. 
\afterpage{
\begin{figure}[!t]
\begin{center}
        \subfigure[][Carnatic music: No. of valid relation types]{%
		 \includegraphics[width=0.45\linewidth]{../../data/results/qualitative/semantic-relation-extraction/carnatic_music.pdf}
		 \label{fig:qual-semantic-relex-carnatic}
        }% 
        \qquad
        \subfigure[][Carnatic music: No. of corresponding assertions]{%
		 \includegraphics[width=0.45\linewidth]{../../data/results/qualitative/semantic-relation-extraction/carnatic_music-relcount.pdf}
		 \label{fig:qual-semantic-relex-carnatic-relcount}
        }%
        \\
        \subfigure[][Hindustani music: No. of valid relation types]{%
		 \includegraphics[width=0.45\linewidth]{../../data/results/qualitative/semantic-relation-extraction/hindustani_music.pdf}
		 \label{fig:qual-semantic-relex-hindustani}
        }%
        \qquad
        \subfigure[][Hindustani music: No. of corresponding assertions]{%
		 \includegraphics[width=0.45\linewidth]{../../data/results/qualitative/semantic-relation-extraction/hindustani_music-relcount.pdf}
		 \label{fig:qual-semantic-relex-hindustani-relcount}
        }%
\end{center}
\caption{Semantic relation extraction task: The number of valid relation types marked for each concept, and the number of corresponding assertions that include the entities in the domain.}
\label{fig:qual-semantic-relex}
\end{figure}
}

@@

\paragraph{Semantic relation extraction.}
For the purpose of this task, the subsumption relation types and also those relation phrases which do not have a consistent meaning across the assertions were discarded. Then, following the procedure discussed in sec.\ref{sec:framework}, we have marked the valid relation types for each concept, and obtained the corresponding assertions featuring the entities in the domain. Fig.~\ref{fig:qual-semantic-relex} shows the results, for both Carnatic and Hindustani music.

@@

A particular limitation of the framework that is of concern is the availability of groudtruth for qualitative evaluation. The current framework hinges on to the structured content in Wikipedia/DBpedia to this extent. However, as our case study with Indian art music shows, they lack finer segregation of concepts (refer to the ontologies linked with this paper). As we have seen, the results from the quantitative and the qualitative evaluation have a strong agreement with each other. We would like to further explore this correlation using other domains, in order to better understand it and adapt the framework to meet this challenge.

>>>>

\usepackage{subfigure}
\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{graphicx}
\usepackage[numbers, sectionbib]{natbib}
\usepackage{tabularx, environ}
\usepackage{multirow}
\usepackage{afterpage}

@@

@@

The second method for the evaluation of concept assignment employs bootstrapping as discussed in sec.~\ref{sec:framework}. This process involves selection of a seedset and determining the number of bootstrapping iterations. For the sake of brevity, we have set the size of seedset to be the same for all the concepts, which is 3. The entities in the seedset are randomly chosen from the ones among the reference data taken from Wikipedia. However, as the bootstrapping process itself can be sensitive to the initial selection of the entities in the seedset, the whole process is repeated 5 times with randomly chosen seedsets. The bootstrapping method is terminated once the size of seedset reaches that of the corresponding concept in the reference data. After every 5 instances added during the process, we measure the overlap ($O$) and residual ($R$) portions of the seedset with respect to the reference data.  Figs.~\ref{fig:qual-object-bootstrapping-carnatic} and \ref{fig:qual-object-bootstrapping-hindustani} show their mean over 5 runs.

\afterpage{
\begin{table}[t]
\begin{center}
\begin{tabularx}{1\textwidth}{lllc|c|c|c|c|c|c}
\noalign{\hrule height 1.1pt}
            &  &  & \textbf{Mus.} & \textbf{Ragas} & \textbf{Sing.} & \textbf{Compositions} & \textbf{Instru.} & \textbf{Composers} & \textbf{Overall} \\
\hline

\multirow{6}{*}{\textbf{Carnatic}} & \multirow{3}{*}{\textbf{\#Rel.types}} 
									  & R & 10 & 5 & 3 & 0 & 5 & 3 & 17 \\
                  &                   & O & 10 & 6 & 5 & 0 & 10 & 6 & 19 \\
                  &                   & S & 12 & 7 & 10 & 0 & 9 & 7 & 27 \\
                  \cline{2-10}
                  & \multirow{3}{*}{\textbf{\#Assertions}} 
					 				  & R & 100 & 30 & 60 & 0 & 70 & 50 & 310 \\
                  &                   & O & 240 & 120 & 160 & 0 & 230 & 160 & 910 \\
                  &                   & S & 220 & 190 & 180 & 0 & 170 & 180 & 940 \\
                  \cline{1-10}
\multirow{6}{*}{\textbf{Hindustani}} & \multirow{3}{*}{\textbf{\#Rel.types}} 
                  					  & R & 8 & 0 & 7 & n/a & 12 & 1 & 18 \\
                  &                   & O & 8 & 0 & 9 & n/a & 9 & 2 & 12 \\
                  &                   & S & 12 & 0 & 12 & n/a & 12 & 2 & 22 \\
                  \cline{2-10}
                  & \multirow{3}{*}{\textbf{\#Assertions}} 
                  					  & R & 140 & 0 & 130 & n/a & 150 & 10 & 430 \\
                  &                   & O & 310 & 0 & 310 & n/a & 320 & 150 & 1090 \\
                  &                   & S & 290 & 0 & 260 & n/a & 280 & 150 & 880 \\
\noalign{\hrule height 1.1pt}
\end{tabularx}
\end{center}
\caption{Semantic relation extraction task: The number of valid relation types marked for each
concept, and the number of corresponding assertions that include the entities in the domain. R, O and S stand for ReVerb, OpenIE4.0 and Sem. Parsing systems respectively.}
\label{tab:qual-semantic-relex}
\end{table}
}

%\afterpage{
%\begin{figure}[!t]
%\begin{center}
%        \subfigure[][Carnatic music: No. of valid relation types]{%
%		 \includegraphics[width=0.45\linewidth]{../../data/results/qualitative/semantic-relation-extraction/carnatic_music.pdf}
%		 \label{fig:qual-semantic-relex-carnatic}
%        }% 
%        \qquad
%        \subfigure[][Carnatic music: No. of corresponding assertions]{%
%		 \includegraphics[width=0.45\linewidth]{../../data/results/qualitative/semantic-relation-extraction/carnatic_music-relcount.pdf}
%		 \label{fig:qual-semantic-relex-carnatic-relcount}
%        }%
%        \\
%        \subfigure[][Hindustani music: No. of valid relation types]{%
%		 \includegraphics[width=0.45\linewidth]{../../data/results/qualitative/semantic-relation-extraction/hindustani_music.pdf}
%		 \label{fig:qual-semantic-relex-hindustani}
%        }%
%        \qquad
%        \subfigure[][Hindustani music: No. of corresponding assertions]{%
%		 \includegraphics[width=0.45\linewidth]{../../data/results/qualitative/semantic-relation-extraction/hindustani_music-relcount.pdf}
%		 \label{fig:qual-semantic-relex-hindustani-relcount}
%        }%
%\end{center}
%\caption{Semantic relation extraction task: The number of valid relation types marked for each concept, and the number of corresponding assertions that include the entities in the domain.}
%\label{fig:qual-semantic-relex}
%\end{figure}
%}

@@

\paragraph{Semantic relation extraction.}
For the purpose of this task, the subsumption relation types and also those relation phrases which do not have a consistent meaning across the assertions were discarded. Then, following the procedure discussed in sec.\ref{sec:framework}, we have marked the valid relation types for each concept, and obtained the corresponding assertions featuring the entities in the domain. Table.~\ref{tab:qual-semantic-relex} shows the results, for both Carnatic and Hindustani music.

@@

A particular limitation of the framework that is of concern is the availability of groudtruth for qualitative evaluation. The current framework hinges on to the structured content in Wikipedia/DBpedia to this extent. However, as our case study with Indian art music shows, they lack finer segregation of concepts (refer to the ontologies linked to in this paper). As we have seen, the results from the quantitative and the qualitative evaluation have a strong agreement with each other. We would like to further explore this correlation using other domains, in order to better understand it and adapt the framework to meet this challenge.
